A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol

### 2023-04-04 paper.Rmd
section 5.5 revised

We have also investigated the impact of different heteroskedasticity shapes on power of conventional tests and visual tests. In theory, the "left-triangle" and the "right-triangle" shapes are functionally identical from the point of view of a Breusch-Pagan test. As shown in Figure \ref{fig:heter-power-uniform-a}, this is indeed the case where little difference between the power curves can be perceived. Similarly, visual tests should have the same power in detecting these two shapes if they are equally likely to be identified. However, it can be observed from Figure \ref{fig:heter-power-uniform-a} that the power curve of the "left-triangle" shape is higher than the one of the "right-triangle" shape, indicating a potential favour of orientation by human, which is worth to be explored in future studies. Besides, the chance of detecting the "butterfly" shape are higher than other two shapes in both conventional and visual testing.

```{r heter-power-uniform-a, fig.height = 4, fig.cap = 'Power of conventional tests and visual tests on lineups produced by the heteroskedasticity model with three different shapes controlled by the parameter $a$. The visual test has an asymmetric power in testing the "left-triangle" shape and "right-triangle" shape, while these two shapes are equivalent in conventional testing.'}

>>>>

Figure \ref{fig:heter-power-uniform-a} examines the impact of the shape of the heteroskedasticity on the power of of both tests. The butterfly shape has higher power on both types of tests. The "left-triangle" and the "right-triangle" shapes are functionally identical, and this is observed for the conventional test, where the power curves are identical. Interestingly there is a difference for the visual test, where the power curve of the "left-triangle" shape is slightly higher than that of the "right-triangle" shape. This indicates a bias in perceiving heteroskedasticity depending on the direction. This would be worth investigating further.

```{r heter-power-uniform-a, fig.height = 4, fig.cap = 'The effect of heteroskedasticity shape (parameter $a$) on the power of conventional and visual tests. The butterfly has higher power in both tests. Curiously, the visual test has slightly higher power for the "left-triangle" than the "right-triangle" shape, when it would be expected that they should be identical, which is observed in conventional testing.'}

### 2023-04-04 paper.tex
section 5.5 revised

We have also investigated the impact of different heteroskedasticity
shapes on power of conventional tests and visual tests. In theory, the
``left-triangle'' and the ``right-triangle'' shapes are functionally
identical from the point of view of a Breusch-Pagan test. As shown in
Figure \ref{fig:heter-power-uniform-a}, this is indeed the case where
little difference between the power curves can be perceived. Similarly,
visual tests should have the same power in detecting these two shapes if
they are equally likely to be identified. However, it can be observed
from Figure \ref{fig:heter-power-uniform-a} that the power curve of the
``left-triangle'' shape is higher than the one of the ``right-triangle''
shape, indicating a potential favour of orientation by human, which is
worth to be explored in future studies. Besides, the chance of detecting
the ``butterfly'' shape are higher than other two shapes in both
conventional and visual testing.

@@

\caption{Power of conventional tests and visual tests on lineups produced by the heteroskedasticity model with three different shapes controlled by the parameter $a$. The visual test has an asymmetric power in testing the "left-triangle" shape and "right-triangle" shape, while these two shapes are equivalent in conventional testing.}\label{fig:heter-power-uniform-a}
\end{figure}

>>>>

Figure \ref{fig:heter-power-uniform-a} examines the impact of the shape
of the heteroskedasticity on the power of of both tests. The butterfly
shape has higher power on both types of tests. The ``left-triangle'' and
the ``right-triangle'' shapes are functionally identical, and this is
observed for the conventional test, where the power curves are
identical. Interestingly there is a difference for the visual test,
where the power curve of the ``left-triangle'' shape is slightly higher
than that of the ``right-triangle'' shape. This indicates a bias in
perceiving heteroskedasticity depending on the direction. This would be
worth investigating further.

@@

\caption{The effect of heteroskedasticity shape (parameter $a$) on the power of conventional and visual tests. The butterfly has higher power in both tests. Curiously, the visual test has slightly higher power for the "left-triangle" than the "right-triangle" shape, when it would be expected that they should be identical, which is observed in conventional testing.}\label{fig:heter-power-uniform-a}
\end{figure}
